
The followings are the most used functions in the DRtree package:
\begin{itemize}
	\item
	{\bf void DR\_Init(void)}:\\
	This function initializes the DRtree package. It must be called before
	any other function in the DRtree package.

	\item
	{\bf int DR\_CreateIndex(char *filename, int dim, coord\_t ctype)}:\\
	This function creates a DR index file. The created index file will have
	the name as {\em filename}, with dimension {\em dim} and coordinate type
	{\em ctype} ({\tt int} or {\tt float}).
	It returns 0 when everything is OK or a negative error number otherwise.

	\item
	{\bf int DR\_DestroyIndex(char *filename)}:\\
	This function deletes a DR index file with the name as {\em filename}.
	It returns 0 when everything is OK or a negative error number otherwise.

	\item
	{\bf int DR\_OpenIndex(char *filename)}:\\
	This function opens a DR index file with the name as {\em filename}.
	It returns an index descriptor when everything is OK or a
	negative error number otherwise.

	\item
	{\bf int DR\_CloseIndex(int fd)}:\\
	This function closes a DR index file with the descriptor as {\em fd}.
	It returns 0 when everything is OK or a negative error number otherwise.

	\item
	{\bf int DR\_SearchEntry(int fd, DRrect *testrect)}:\\
	This function searches in a DR index with the descriptor {\em fd} for
	every record whose covering rectangle overlaps with {\em testrect}.
	It returns the number of qualified records or an error number otherwise.

	\item
	{\bf int DR\_InsertEntry(int fd, int childno, DRrect *childcov)}:\\
	This function inserts into a DR index with the descriptor {\em fd} a
	record whose ID number is {\em childno} and the covering rectangle
	is {\em childcov}.
	It returns 0 when everything is OK or a negative error number otherwise.

	\item
	{\bf int DR\_DeleteEntry(int fd, int childno, DRrect *testrect)}:\\
	This function deletes from a DR index with the descriptor {\em fd} a
	record whose ID number is {\em childno} and whose covering rectangle
	overlaps with {\em testrect}. It returns 1 if the record is deleted, 0
	if the record is not found or a negative error number otherwise.

\end{itemize}

